Analyzing Fairness: Race, Recidivism, and the COMPAS Algorithm

### 2022-04-21 final_metrics_analysis.Rmd
wordcloud (how to install wordcloud package: https://stackoverflow.com/questions/47298070/importerror-no-module-named-wordcloud) changed color on mosaic plots

```{python exploratory recidivism mosaic plot}
props={}
props[('Caucasian','Recidivated')]={'facecolor':'red', 'edgecolor':'white'}
props[('Caucasian','Survived')]={'facecolor':'red', 'edgecolor':'white'}
props[('African-American','Recidivated')]={'facecolor':'xkcd:aqua','edgecolor':'white'}
props[('African-American','Survived')]=        {'facecolor':'xkcd:aqua','edgecolor':'white'}
labelizer=lambda k:{('Caucasian','Recidivated'):822,('African-American','Recidivated'):1661,('Caucasian','Survived'):1278,('African-American','Survived'):1512}[k]
mosaic(df_viz,['race','two_year_recid'],labelizer=labelizer,properties=props)
plt.show()
```

@@

>>>>

```{python exploratory recidivism mosaic plot}
props={}
props[('Caucasian','Recidivated')]={'facecolor':'green', 'edgecolor':'white'}
props[('Caucasian','Survived')]={'facecolor':'green', 'edgecolor':'white'}
props[('African-American','Recidivated')]={'facecolor':'xkcd:purple','edgecolor':'white'}
props[('African-American','Survived')]=        {'facecolor':'xkcd:purple','edgecolor':'white'}
labelizer=lambda k:{('Caucasian','Recidivated'):822,('African-American','Recidivated'):1661,('Caucasian','Survived'):1278,('African-American','Survived'):1512}[k]
mosaic(df_viz,['race','two_year_recid'],labelizer=labelizer,properties=props)
plt.show()
```

@@

```{python wordcloud setup}
from os import path
from PIL import Image
from wordcloud import WordCloud, STOPWORDS, ImageColorGenerator
```

```{python wordcloud}
text = " ".join(charge for charge in df_viz.c_charge_desc)
stopwords = set(STOPWORDS)
stopwords.update(["arrest", "case"])
wordcloud = WordCloud(stopwords=stopwords, background_color="white").generate(text)
```

```{python wordcloud image}
plt.imshow(wordcloud, interpolation='bilinear')
plt.axis("off")
plt.show()
```
